---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
library(data.table)
library(ggplot2)

```

Type any R code in the chunk, for example:
```{r}
setwd('/Users/emilyziyixiao/DataspellProjects/ResearchDesignHW')

data <- read.csv('online_dating.csv',stringsAsFactors = TRUE)

summary(data)
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
```{r}

age2020 <- data[data$year == 'Year 2020', 'age']
age2021 <- data[data$year == 'Year 2021', 'age']

t.test(age2020, age2021, alternative = "two.sided", var.equal = FALSE)

```
```{r}
rev2020 <- data[data$year == 'Year 2020', 'revenue']
rev2021 <- data[data$year == 'Year 2021', 'revenue']

t.test(rev2020, rev2021, alternative = "two.sided", var.equal = FALSE)
```
```{r}
under3 <- data[data$daily_messages < 3, "year"]
atleast3lessthan5 <- data[data$daily_messages > 3 & data$daily_messages < 5, "year"]
atleast5 <- data[data$daily_messages > 5, "year"]

#table(under3, atleast3lessthan5, atleast5)
summary(under3)
summary(atleast3lessthan5)
summary(atleast5)
```
